Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-26 Docs/IJES/journal.tex
review 4.6 Analysis of the partitioning problem using

Algorithm of Figure~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions, as seen in~\cite{Bjorner2014}. A $\nu$Z logical context must firstly be created (line $2$), in order to add constraints and to check whether a given model exists to the set of constraints. Note that the number of nodes and edges, software, hardware, and communications costs as well as the incidence matrix E must also be declared.

>>>>

Algorithm of Figure~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions, as described in~\cite{Bjorner2014}. A $\nu$Z logical context must firstly be created (line $2$), in order to add constraints and to check whether a given model exists to the constraints set. Note that the number of nodes and edges, software, hardware, and communications costs as well as the incidence matrix E must also be declared.
